When are Fuzzy Extractors Possible?

### 2014-09-24 trunk/info-bounds/FuzzyExtPossibility.tex
working on isoparametric inequality proof

\subsection{Impossibility of info-theoretic sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

@@

\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
\end{proposition}
\begin{proof}
Consider some $w\in V$.  Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.  The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
\end{proof}
\begin{lemma}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  We will however, not consider these coins in our security analysis.

@@

Consider some $p\in A_{ss}$.  We now show that $H_0(V | p) \le n-\log |B_t|$.  Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.  Thus for every value in $V|p$ this is also true.  This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|p$ is a set with minimum distance at least $t$.  By the Singleton bound, this implies that $H_0(V | p) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
%By the Markov inequality, 
%\[
%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
%\]
%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
%
%Outline of what I want to say.
%\begin{itemize}
%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.  Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).  
%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
%\end{itemize}
\end{proof}
We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.

@@

\subsection{Computational secure sketches}
We do not consider a computational version of secure sketches. Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.

\begin{corollary}
This is also impossible for computational sketches that retain hill entropy.\bnote{fill this in, use asiacrypt result.}
\end{corollary}

%\subsection{Conductors}
%Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
%\begin{lemma}
%Not possible for information-theoretic objects.
%\end{lemma}
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\subsection{Fuzzy min-entropy is not sufficient for secure sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

@@

\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\gamma$.
\end{proposition}
\begin{proof}
Consider some $w\in V$.  Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.  The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
\end{proof}
\begin{lemma}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  We do not consider these coins in our security analysis~(and thus, they can be considered private).

@@

Consider some $p\in A_{ss}$.  We now show that $H_0(V | p) \le (\gamma-t+1)\log |\mathbb{F}|$.  Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.  Thus for every value in $V|p$ this is also true.  This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|p$ is a set with minimum distance at least $t$.  By the Singleton bound, this implies that $H_0(V | p) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
%By the Markov inequality, 
%\[
%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
%\]
%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
%
%Outline of what I want to say.
%\begin{itemize}
%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.  Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).  
%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
%\end{itemize}
\end{proof}
We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.

@@

\subsubsection{Computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses HILL entropy.

HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  Fuller et al.~use a weak version due to Gentry and Wichs~\cite{gentry2011separating}.

\begin{definition}
\label{def:relaxed hill}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}$.
\end{definition}

A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $s_{sec}, \epsilon_{sec}$ parameters to the definition, representing the distinguishing circuit).  By applying the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:

\begin{corollary}
\label{cor:imposs comp sketch}
Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.  There exists a family of distributions $\mathcal{V}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.  If 
\begin{itemize}
\item $s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
\item $t\ge 4$,
\item and $\epsilon + t\delta < 1/16$,
\end{itemize}
 then $\tilde{m} =O(1)$.
\end{corollary}

%\begin{corollary}
%\label{cor:rec yields sketch}
%Let $\mathcal{Z}$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
%$4(\epsilon+t\delta)$. 
%\end{corollary}

\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).  Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.

\section{Distribution-Oblivious Fuzzy Extractors}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  In this section, we extend this result to fuzzy extractors.  The main difficulty is showing that fuzzy extractors must cause a significantly entropy drop in $V$.  This is not true for all metric spaces.  We begin with the case of perfect correctness in the Hamming metric.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$ for $\tilde{m} =\omega(1)$ for $t\ge 4$. \bnote{what is $\epsilon$? what are the other parameters?}
\end{theorem}
 \bnote{write a proof!}
\begin{proof}
The only difference between \thref{thm:imposs fuzz ext} and \thref{thm:imposs sketch} is the functionality required of the algorithms $(\gen, \rep)$.  Thus, we must prove that a fuzzy extractor must still cause a significant drop in the entropy of $V$:

\begin{lemma}
Fix some $(\gen, \rep)$ algorithm with $\kappa = \omega(\log n)$ and $\epsilon=$ \bnote{what is this?}.  Then $\tilde{H}_0(V | \gen(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.
\end{lemma}
\begin{proof}
We assume that $\rep$ is deterministic in our analysis.  Any randomness necessary for the \rep algorithm can be provided by $\gen$.  We do not consider these coins in our security analysis~(and thus, they can be considered private).  Denote by $(R, P) \leftarrow \gen(V)$.

%By the definition of correctness for $(\sketch, \rec)$, 
%\[
%\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
%\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
%Fix some $w$.  
By Markov's inequality, there exists a set $A_{p}$ such that $\Pr[p\in A_{p}]\ge 1/2$ and $\forall p\in A_{p}$, 
\[
(R |P =p, P = p ) \approx_{2\epsilon} (U_\kappa , P =p).
\]
%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $p^*\in A_{ss}$.  We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.  Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p$ is at least $(1-2\epsilon)2^\kappa$.  Note that, $R|P=p$ is the set of possible keys.

The set of possible keys induces a partition on the metric space.  That is, for every $w\in\mathcal{M}$, there exists a unique $Q_{p^*,r}$ such that $\rep(w, p^*) =r$.  Define two sets, called the boundary and interior respectively: \begin{align*}
\bnd(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\},\\
\inter(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =r\}.
\end{align*}

Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$.  Furthermore, note that for any $r\in \zo^\kappa$,  $ | Q_{p^*, r}| \le (1+\epsilon)2^\kappa.$\bnote{need to fill in this distinguishing argument, note this doesn't need to be the case for all $p^*$ just on average. need another markov inequality.}\bnote{what can we say about the relative sizes of these spaces?}

We now consider the distribution of $V | P=p^*$.  By the functionality of $(\gen, \rep)$, for every $v\in V| P=p^*$, $v\in Int(Q_{p, r})$.  Furthermore, if $v$ is not in some interior then $v\not \in V | P=p^*$.  Thus, it suffices to show that $\frac{\sum_{r} |\inter(Q_{p^*, r})|}{\mathcal{M}} = XXX$\bnote{fill this in.}

To show this we any such partitioning of the metric space must have the majority of points lying on the boundary.  This is true for the Hamming metric.
\begin{lemma}[Isoparametric Inequality]
\bnote{XXXX}
\end{lemma}
\end{proof}
\end{proof}

\bibliographystyle{alpha}
\bibliography{crypto}
